\expandafter\newcommand\csname myqq1\endcsname{ [162] The Maluku Islands were controlled by the Dutch,[V] but in 1810 during the Napoleonic Wars British troops briefly captured the Banda Islands, seizing nutmeg trees which they subsequently planted in Ceylon.  [23] Although the museum's management had traditionally been dominated by classicists and antiquarians,[24] in 1856 the natural history department was split into separate departments of botany, zoology, mineralogy and geology, each with their own keeper and with botanist and palaeontologist Richard Owen as superintendent of the four departments.}
\expandafter\newcommand\csname myqq2\endcsname{ Digitalis purpurea, common foxglove,[182] has been a medicinal plant for millennia.}
\expandafter\newcommand\csname myqq3\endcsname{ "Frivolous" and "vexatious" generally mean different things, however both are typically grouped together as they relate to the same basic concept of a complaint or claim not being brought in good faith: 
 It is a single story building with an attic, which has been converted to include dormer windows. }
\expandafter\newcommand\csname myqq4\endcsname{ After an online petition, the council decided that the structure could remain for two years.  [27] There had also long been criticism that because of the varied nature of its displays the museum was confusing and lacked coherence; as early as 1824 Sir Robert Peel, the Home Secretary, had commented that "what with marbles, statues, butterflies, manuscripts, books and pictures, I think the museum is a farrago that distracts attention".}
\expandafter\newcommand\csname myqq5\endcsname{ Pyrus indica (now Docynia indica), the Indian pear.  Able to grow in a wide variety of climates, by the time the museum was built it was cultivated worldwide.}
\expandafter\newcommand\csname myqq6\endcsname{ The chief idea to be represented is that of growth. }
\expandafter\newcommand\csname myqq7\endcsname{ Saccharum officinarum, the most common species of sugarcane, at the time the primary source of sugar.}
\expandafter\newcommand\csname myqq8\endcsname{ Butea frondosa, flame-of-the-forest or dhaak,[112] an Indian plant whose sap was an important source of tannin.}
\expandafter\newcommand\csname myqq9\endcsname{ Butea frondosa, flame-of-the-forest or dhaak,[112] an Indian plant whose sap was an important source of tannin.  [100] Tobacco from Nicotiana rustica (Aztec tobacco) had been introduced to England from the failed Roanoke Colony, the first British attempt at permanent settlement in North America, but the taste proved unpopular in European markets.}
\expandafter\newcommand\csname myqq10\endcsname{ •  •  As a consequence of the trade deficit in silver, the East India Company began to pay for these goods with opium grown in its Indian territories, in violation of Chinese law.  •  Sloane's chocolate milk was intended for medicinal use, in particular as a believed cure for tuberculosis and fainting fits.}
\expandafter\newcommand\csname myqq11\endcsname{ Global uses of sunflower seed (from FAO data)
 [180] It grows in the wild throughout the British Isles and Europe.  [123] It is likely that Waterhouse and the devoutly religious Owen included this plant owing to its religious significance.}
\expandafter\newcommand\csname myqq12\endcsname{ The flow of the Kochechum strongly depends on the season, approaching zero in early spring and reaching its maximum in June.[ Sunflower seed in the context of global oilseed production (FAO data)}
\expandafter\newcommand\csname myqq13\endcsname{ [5] It is known as Sqump to its regulars, the Square and Compass was popular amongst the Telecommunications Research Establishment scientists in Purbeck, who knew the inn as Sine and Cosine.  The permafrost effectively blocks any underground supply; all water flowing through the river comes from snow and rain.  [93] The height of the Central Hall ceiling made this a complicated and expensive process, requiring floor-to-ceiling scaffolding across the length and width of the Central Hall.  Scientists are using this group to make “bridging crosses” that will bring together the genes from the crop sunflower and several other perennial species.  }
\expandafter\newcommand\csname myqq14\endcsname{ The walls and the ceilings are decorated, as befits a Palace of Nature, with all the varieties of animal and vegetable life, and the more striking fossil remains .  1 Deterioration, restoration and conservation}
\expandafter\newcommand\csname myqq15\endcsname{ This crop plant (now called by the misleading name Jerusalem artichoke) was grown for its tubers and not for its seed.   suis lay 3–6 eggs per day following a blood meal and mating, eventually laying about 90 eggs.  [55] A smaller North Hall, immediately north of the Central Hall, would be used for exhibits specifically relating to British natural history.}
\expandafter\newcommand\csname myqq16\endcsname{ A tiny proportion of the global sunflower crop is directly eaten as “nuts” or kernels.  
 It is a right and most significant tributary of the Nizhnyaya Tunguska. }
\expandafter\newcommand\csname myqq17\endcsname{ [4] In 2014, the Square and Compass won the Good Pub Guide's award for Unspoilt Pub of the Year.  Unlike the cavernous, intentionally cathedral-like feel of the main space of the Central Hall,[68] the ceiling of the landing above the main entrance, connecting the balconies to the upper level, has a different design.}
\expandafter\newcommand\csname myqq18\endcsname{ The walls and the ceilings are decorated, as befits a Palace of Nature, with all the varieties of animal and vegetable life, and the more striking fossil remains .  In 2017 a blue whale skeleton was suspended from the ceiling of the recently renamed Hintze Hall, replacing the "Dippy" Diplodocus cast which had stood there for many years.}
\expandafter\newcommand\csname myqq19\endcsname{ [107] The economic benefits of tobacco farming led to the colony prospering and to British expansion along the coast of North America, while the labour-intensive processes involved in tobacco production led to Britain entering the Atlantic slave trade.  Researchers at The Land Institute have made many tetraploid hybrids like the ones shown here.   [126] In the 19th century the popularity of sugar continued to rise; over the fifty years from 1800 to 1850 the per capita British consumption of sugar doubled.}
\expandafter\newcommand\csname myqq20\endcsname{ A vexatious claim or complaint is one (or a series of many) that is specifically being pressed on to cause an act of harassment, annoyance, frustration, worry, or even bring financial cost (such as engage a defence lawyer) to their defendant or respondent.  Thus strong π backbonding causes a metal-alkene complex to assume the character of a metallacyclopropane.  Sunflower seed in the context of global oilseed production (FAO data)}
\expandafter\newcommand\csname myqq21\endcsname{ The archaic panels' style remains the same, but each lower panel depicts a separate species. 
 Unlike the intentionally exposed girders of the main hall, the supporting arches above the landing are enclosed within terracotta facing. }
\expandafter\newcommand\csname myqq22\endcsname{ Every civilized state in Europe possesses such a Museum.   [28][G] In January 1860, the trustees of the museum approved Owen's proposal.}
\expandafter\newcommand\csname myqq23\endcsname{ Lonicera periclymenum, woodbine or common honeysuckle,[171] is highly valued as an ornamental plant, and has one of the sweetest floral scents of any native British plant.  Often a "frivolous" claim is one about a matter so trivial, one so meritless on its face, or one without substance that investigation would be disproportionate in terms of time and cost. }
\expandafter\newcommand\csname myqq24\endcsname{ One of the identical twin balconies running the length of Central Hall, connecting the first and second staircases
 One of the identical twin balconies running the length of Central Hall, connecting the first and second staircases}
\expandafter\newcommand\csname myqq25\endcsname{ •  •  A lack of funds meant that Waterhouse's planned east, west and north galleries were never built, and the central halls and south front were the only parts of his design to be completed.}
\expandafter\newcommand\csname myqq26\endcsname{ The IFC scrutinised and monitored the performance of the Football Association, the FA Premier League and the Football League and issued publicly available reports on its findings. 
 The election followed the resignation of former President Eduard Shevardnadze.  Painting by Waterhouse of the final design for the building, 1876. }
\expandafter\newcommand\csname myqq27\endcsname{ The cracks in the plasterwork were filled, and flaked or peeling paintwork was repaired with Japanese tissue.  At the time the museum was built it was also in common use as a herbal remedy.}
\expandafter\newcommand\csname myqq28\endcsname{ Pyrus malus, the apple tree,[169] had for centuries been a staple fruit of the British diet.}
\expandafter\newcommand\csname myqq29\endcsname{ 1 Sunflower seed: current production and uses}
\expandafter\newcommand\csname myqq30\endcsname{ Rhizomes enable a plant to spread into new territory. }
\expandafter\newcommand\csname myqq31\endcsname{ [159] A strong laxative, in the 19th century it formed the basis of many European and traditional Indian medicines.}
\expandafter\newcommand\csname myqq32\endcsname{ Magnolia auriculata, the big-leaf magnolia (now called Magnolia fraseri),[112] was native to the Blue Ridge Mountains in the Appalachians. }
\expandafter\newcommand\csname myqq33\endcsname{ [171] Aconitum napellus napellus, the subspecies found in Britain, is one of the few plants endemic to Britain.}
\expandafter\newcommand\csname myqq34\endcsname{ [140] Knapp \& Press (2005) contend that this tree, with which British visitors were unlikely to have been familiar, was intentionally included among more familiar plants as a device to attract the attention of viewers.  [80] Some of the archaic panels appear to be simplified versions of the illustrations in Nathaniel Wallich's book Plantae Asiaticae Rariores.  •  •  The original refreshment room had been on the balcony level between the Central and North Halls.}
\expandafter\newcommand\csname myqq35\endcsname{ [123] Its distinctive fruit would have been immediately recognisable to 19th-century viewers, serving to attract viewers to examine the ceiling more closely.  •  •  The delay between the selection of the site in 1864 and the acceptance of Waterhouse's design in 1868 was the result of repeated changes of government; the United Kingdom had five different prime ministers during this period, each of whom had a different opinion on the controversial scheme to build a major museum in what was then a distant and relatively inaccessible suburb.  [137] Although not native to Britain, visitors would have been familiar with grapes from the manufacture of wine, at the time considered a luxury.  With more space for displays and able to accommodate large numbers of visitors, the new British Museum proved a success with the public, and the natural history department proved particularly popular.}
\expandafter\newcommand\csname myqq36\endcsname{ [40] In 1873 construction finally began on the new museum building.}
\expandafter\newcommand\csname myqq37\endcsname{ •  •  The delay between the selection of the site in 1864 and the acceptance of Waterhouse's design in 1868 was the result of repeated changes of government; the United Kingdom had five different prime ministers during this period, each of whom had a different opinion on the controversial scheme to build a major museum in what was then a distant and relatively inaccessible suburb.  Lonicera periclymenum, woodbine or common honeysuckle,[171] is highly valued as an ornamental plant, and has one of the sweetest floral scents of any native British plant.}
\expandafter\newcommand\csname myqq38\endcsname{ Rhizomes enable a plant to spread into new territory. }
\expandafter\newcommand\csname myqq39\endcsname{ Panels from the balcony ceiling, with a lizard, snail, bird and crab}
\expandafter\newcommand\csname myqq40\endcsname{ 1 Sunflower seed: current production and uses
 The term is not defined in statute law, but has been defined in legal cases. }
\expandafter\newcommand\csname myqq41\endcsname{ A tiny proportion of the global sunflower crop is directly eaten as “nuts” or kernels.  }
\expandafter\newcommand\csname myqq42\endcsname{ One of the identical twin balconies running the length of Central Hall, connecting the first and second staircases
 [84] Unlike the archaic panels in the top row of the Central Hall, the upper rows on each side consist of plain green panels, each containing a heraldic rose, thistle or shamrock in representation of England, Scotland and Ireland, the three nations then constituting the constituent parts of the United Kingdom.}
\expandafter\newcommand\csname myqq43\endcsname{ [73] The central column in the lowest row depicts the trunk or stalk of the plant in question, while the panels on either side and the three panels of the row above depict the branches of the plant spreading from the lower central panel.}
\expandafter\newcommand\csname myqq44\endcsname{ Between the main entrance and the landing of the main staircase,[75] the lower two rows of panels all have a pale cream background, intended to draw the viewer's attention to the plant being illustrated; each plant chosen was considered significant either to visitors, or to the museum itself.  [156] (The scientific name Blighia sapida had been given to the ackee by staff at the British Museum, so the museum's staff would certainly have been aware of the correct name. }
\expandafter\newcommand\csname myqq45\endcsname{ The IFC scrutinised and monitored the performance of the Football Association, the FA Premier League and the Football League and issued publicly available reports on its findings. }
\expandafter\newcommand\csname myqq46\endcsname{ Records do not survive of how the plants to be represented were chosen and who created the initial designs.  Quercus tinctoria, the black oak (now called Quercus velutina),[112] is a North American species that was endemic in most of the former British American colonies.  Scientists are using this group to make “bridging crosses” that will bring together the genes from the crop sunflower and several other perennial species.  }
\expandafter\newcommand\csname myqq47\endcsname{ Archaic panel depicting Ottelia and a stylised bird
 A presidential election was held in the Republic of Georgia on January 4, 2004.}
\expandafter\newcommand\csname myqq48\endcsname{ Olea europea, the olive tree,[168] was at the time almost unknown in Britain; they did not grow in the British climate, and both olives and olive oil were rarely used in British cookery.   The Square and Compass was built in the 18th century of rubble stone walls, stone chimney stacks and a stone stale roof.   One of the identical twin balconies running the length of Central Hall, connecting the first and second staircases}
\expandafter\newcommand\csname myqq49\endcsname{ [98] The ends of the Central Hall suffered the worst deterioration, with some cracks above the landing and the northern end of the hall becoming large enough to be visible to the naked eye, while the gilding in the North Hall became gradually tarnished.  [10][C] Parliament ultimately agreed to establish a national lottery to fund the purchase of Sloane's collection and the Harleian Library which was also currently for sale, and to unite them with the Cotton library, which had been bequeathed to the nation in 1702, to create a national collection.}
\expandafter\newcommand\csname myqq50\endcsname{ [93] In 1924 and 1975, the museum has been obliged to repair and restore the ceilings owing to water damage.  The confluence of Kochechum and Nizhnyaya Tunguska corresponds to the farthest point of fairway section upstream off the Yenisey. }
\expandafter\newcommand\csname myqq51\endcsname{ These plants are remarkably diverse in appearance, including variation for head size, color, leaf shape, height.   Because the louse have neither free-living stages nor vectors for infection of H.}
\expandafter\newcommand\csname myqq52\endcsname{ [150] The first citrus fruit to be cultivated,[155] since antiquity citrons had been an important ingredient in many medications.  [27] There had also long been criticism that because of the varied nature of its displays the museum was confusing and lacked coherence; as early as 1824 Sir Robert Peel, the Home Secretary, had commented that "what with marbles, statues, butterflies, manuscripts, books and pictures, I think the museum is a farrago that distracts attention".}
\expandafter\newcommand\csname myqq53\endcsname{ It is possible that it was included as a tribute to Hans Sloane.  [181] A popular ornamental plant, it has spread from gardens and grows wild throughout Britain.}
\expandafter\newcommand\csname myqq54\endcsname{ Prunus amygdalus, the almond,[112] was religiously significant in Christianity, being described in the Bible as among "the best fruits in the land".  Ranunculus lingua, greater spearwort,[176] is a close relative of the better-known buttercup.}
\expandafter\newcommand\csname myqq55\endcsname{ Prunus amygdalus, the almond,[112] was religiously significant in Christianity, being described in the Bible as among "the best fruits in the land".}
\expandafter\newcommand\csname myqq56\endcsname{ Many sunflower species can be artificially hybridized but one group of wild perennial species cross, the hexaploids (six copies of all chromosomes instead of the usual two copies) are especially easy to cross.   Banks persuaded Cook to call his landing site Botany Bay, on account of the wide variety of specimens he collected there; Cook had intended to call the site Stingray Bay.  [89][Q] Much was written at the time of the museum's opening about the terracotta decorations of the museum, but very little was written about how the ceiling was received.}
\expandafter\newcommand\csname myqq57\endcsname{ A northern lobby ceiling depicting birds, insects, butterflies and paterae}
\expandafter\newcommand\csname myqq58\endcsname{ [166] As with the orange, lemons rarely grew in Britain, but were also popular in British cuisine.}
\expandafter\newcommand\csname myqq59\endcsname{ Together with her dotty grandma and her crazy uncle, she tries to help securing the family's income.  [28] Owen proposed that the museum be split into separate buildings, with one building to house the works of Man (art, antiquities, books and manuscripts) and one to house the works of God (the natural history departments);[29] he argued that the expansion of the British Empire had led to an increased ability to procure specimens, and that increased space to store and display these specimens would both aid scholarship, and enhance Britain's prestige.}
\expandafter\newcommand\csname myqq60\endcsname{ [121] Although historically sugar was rarely used in Britain, it became hugely popular in the 18th century; in 1750 sugar constituted around one fifth of all European imports, and the overwhelming majority of these imports came from British and French slave plantations in the Caribbean.}
\expandafter\newcommand\csname myqq61\endcsname{ Panels from the balcony ceiling, with a lizard, snail, bird and crab
 In law, frivolous or vexatious, is a term used to challenge a complaint or a legal proceeding being heard, or to deny or dismiss or strike out any ensuing judicial or non-judicial processes.  }
\expandafter\newcommand\csname myqq62\endcsname{ Early on January 5 Saakashvili claimed victory, although no official figures had been released at that time.}
\expandafter\newcommand\csname myqq63\endcsname{ •  Sloane's chocolate milk was intended for medicinal use, in particular as a believed cure for tuberculosis and fainting fits.  The IFC has been replaced by the Independent Football Ombudsman (IFO), who will act as the final stage in football’s complaints procedure. 
 Once penetrated, the blood is sucked up the food channel by a mechanism located in the louse's head.}
\expandafter\newcommand\csname myqq64\endcsname{ Pinus sylvestris, the Scots pine,[165] Great Britain's only native species of pine.  [64] Having obtained approval for the paintings, Waterhouse managed to convince Ayrton that the paintings' appeal would be enhanced if certain elements were gilded.  Frequently used in English cookery, particularly cherry pie, its distinctive red fruit would have been easily recognised by 19th-century visitors; Knapp \& Press (2005) conjecture that as with the quince, it was included to allow viewers to compare this relatively familiar plant to the less recognisable species also illustrated.}
\expandafter\newcommand\csname myqq65\endcsname{ Olea europea, the olive tree,[168] was at the time almost unknown in Britain; they did not grow in the British climate, and both olives and olive oil were rarely used in British cookery.   1 Metal carbonyls, nitrosyls, and isocyanides
 Knapp \& Press (2005) conjecture that the quince was included to allow visitors to compare a familiar plant with those more exotic species also depicted on the ceiling.}
\expandafter\newcommand\csname myqq66\endcsname{ As the ceilings were built cheaply, they are extremely fragile and require regular repair. }
\expandafter\newcommand\csname myqq67\endcsname{ Frequently used in English cookery, particularly cherry pie, its distinctive red fruit would have been easily recognised by 19th-century visitors; Knapp \& Press (2005) conjecture that as with the quince, it was included to allow viewers to compare this relatively familiar plant to the less recognisable species also illustrated.  [140] Knapp \& Press (2005) contend that this tree, with which British visitors were unlikely to have been familiar, was intentionally included among more familiar plants as a device to attract the attention of viewers.}
\expandafter\newcommand\csname myqq68\endcsname{ There is no bar, instead drinks are served through two serving hatches.   •  •  The delay between the selection of the site in 1864 and the acceptance of Waterhouse's design in 1868 was the result of repeated changes of government; the United Kingdom had five different prime ministers during this period, each of whom had a different opinion on the controversial scheme to build a major museum in what was then a distant and relatively inaccessible suburb.}
\expandafter\newcommand\csname myqq69\endcsname{ Owen, who considered animals more important than plants, was unhappy with the museum containing botanical specimens at all, and during the negotiations that led to the new building supported transferring the botanical collections to the new Royal Botanic Gardens at Kew to amalgamate the national collections of living and preserved plants.  •  •  The delay between the selection of the site in 1864 and the acceptance of Waterhouse's design in 1868 was the result of repeated changes of government; the United Kingdom had five different prime ministers during this period, each of whom had a different opinion on the controversial scheme to build a major museum in what was then a distant and relatively inaccessible suburb.  [177] As a species able to grow in rocky areas and to propagate quickly via rhizomes into areas cleared of other species by burning, during the Second World War it spread rapidly in urban areas destroyed by bombing,[177] gaining rosebay willowherb the nickname of "fireweed" by which it remains frequently known.}
\expandafter\newcommand\csname myqq70\endcsname{ The lower panels will have representations of foliage treated conventionally.   Zea mays, sweetcorn or maize,[159] was the staple food of much of the Americas before European colonisation. }
\expandafter\newcommand\csname myqq71\endcsname{ The public is now fully aware, by the reports that have been published by Parliament, by representations to Government, and by articles in Reviews and other Periodicals, of the present condition of the National Museum of Natural History and of its most pressing requirements.   suis spend most of their time in and around the head region of the hog, specifically the ears.}
\expandafter\newcommand\csname myqq72\endcsname{ Towards his death he claimed that by studying as much of the world as possible he hoped to have a closer understanding of the will of God, but there is little evidence that he was particularly pious during most of the period in which he assembled his collections.  — The Times on the opening of the Natural History Museum, 18 April 1881[33]}
\expandafter\newcommand\csname myqq73\endcsname{ [18] The 1821 bequest of the library of 60,000 books assembled by George III forced the trustees to address the issue, as the bequest was on condition that the collection be displayed in a single room, and Montagu House had no such room available.}
\expandafter\newcommand\csname myqq74\endcsname{ In keeping with Owen's intent that the room be used for a display on the topic of the British Isles,[86] the nine lower panels on each side each illustrate a different plant found in Britain or Ireland.}
\expandafter\newcommand\csname myqq75\endcsname{ [173] Although an introduced species, it has grown wild throughout Britain for centuries.}
\expandafter\newcommand\csname myqq76\endcsname{ The other candidates received less than 2\% each.  Woodhenge, sculpture by landlord, Charlie Newman}
\expandafter\newcommand\csname myqq77\endcsname{ [84] The central (highest) rows on each side consist of plain green panels, each containing a heraldic rose, thistle or shamrock in representation of England, Scotland and Ireland, the three nations then constituting the United Kingdom.  [68] The supporting girders of the ceiling are spaced at every third column of panels, dividing the panels into square blocks of nine;[70] the girders are an integral part of the design, designed to be barely visible from the ground but highly visible from the upper galleries, representing industry working with nature.}
\expandafter\newcommand\csname myqq78\endcsname{ As the ceilings were built cheaply, they are extremely fragile and require regular repair.   The public house includes a small museum which displays fossils and local artefacts.}
\expandafter\newcommand\csname myqq79\endcsname{ Corylus avellana, common hazel,[171] is one of the most widely grown varieties used for commercial hazelnut production.  •  •  The sculptures on the interior and exterior of the building reflect the original layout of its displays. }
\expandafter\newcommand\csname myqq80\endcsname{ It would also have been familiar to the museum's visitors as a plant then in common medicinal use.}
\expandafter\newcommand\csname myqq81\endcsname{ [28] Owen proposed that the museum be split into separate buildings, with one building to house the works of Man (art, antiquities, books and manuscripts) and one to house the works of God (the natural history departments);[29] he argued that the expansion of the British Empire had led to an increased ability to procure specimens, and that increased space to store and display these specimens would both aid scholarship, and enhance Britain's prestige.  Imported to Europe in large quantities, it became a hugely popular ornamental plant.  Pinus sylvestris, the Scots pine,[165] Great Britain's only native species of pine.}
\expandafter\newcommand\csname myqq82\endcsname{ Pyrus cydonia, the quince (now known as Cydonia oblonga),[159] was a commonly eaten food in 19th-century Europe, and was also often grown as an ornamental plant. }
\expandafter\newcommand\csname myqq83\endcsname{ Males also contain an aedeagus, a sperm-transferring organ.[ [151] The establishment of European-controlled treaty ports in the wake of China's defeat made it significantly easier for European merchants to visit China and for Europeans to smuggle items out of China.}
\expandafter\newcommand\csname myqq84\endcsname{ The Square and Compass was built in the 18th century of rubble stone walls, stone chimney stacks and a stone stale roof. }
\expandafter\newcommand\csname myqq85\endcsname{ [161] Indigenous to the Maluku Islands (the Moluccas), it had historically been imported to Europe via land across Asia to the Ottoman Empire and onwards to Venice, and consequently was extremely scarce and expensive; it was the search for new routes to nutmeg markets that prompted the voyages of Vasco da Gama to India,[161] of Christopher Columbus to the Americas,[161] and of John Franklin to the Northwest Passage.}
\expandafter\newcommand\csname myqq86\endcsname{ In 1776 it became 'The Sloop', an alehouse with connections to smuggling.   Lonicera periclymenum, woodbine or common honeysuckle,[171] is highly valued as an ornamental plant, and has one of the sweetest floral scents of any native British plant.  1][5][6] Of the stylets that compose the fascicle, two form the food channel, supported by the maxilla.}
\expandafter\newcommand\csname myqq87\endcsname{ Jerusalem Artichoke: the other perennial sunflower}
\expandafter\newcommand\csname myqq88\endcsname{ It was only in 1975 that the exterior was fully washed, restoring it to Waterhouse and Owen's intended appearance.}
\expandafter\newcommand\csname myqq89\endcsname{ [173] At the time the museum was built it was believed to have originated in East Anglia, but is now thought to be an introduced species.  Montagu House at the time of its transfer to the newly created British Museum
 [174] Jimsonweed was also well known as a powerful hallucinogen; its name originates from an incident in 1676 in which troops stationed in Jamestown during Bacon's Rebellion accidentally ate the plant and "turn'd natural Fools" for eleven days.}
%
\expandafter\newcommand\csname myqq90\endcsname{ Tubers are storage organs and are modified rhizomes.  
 The archaic panels' style remains the same, but each lower panel depicts a separate species. 
 [91] Instead, beneath a slate roof, the ceilings were constructed of lath and plaster. }
\expandafter\newcommand\csname myqq91\endcsname{ [163] First described in Nathaniel Wallich's Plantae Asiaticae Rariores, whose botanical illustrations inspired many of the ceiling's archaic panels, its bright yellow flowers and ability to grow in the British climate made it a popular ornamental plant in the 19th century.  Rosa canina, dog rose,[182] was a common ornamental species.   Theobroma cacao, the cacao tree,[135] did not grow in Britain, but chocolate was highly popular in Britain at the time. }
\expandafter\newcommand\csname myqq92\endcsname{ "The primary tasks to be implemented from the first days of my presidency include introduction of a Prime Minister's post, appointment of a date for parliamentary elections and implementation of anti-corruption measures in the country," Saakashvili said. }
\expandafter\newcommand\csname myqq93\endcsname{ The trustees settled on Montagu House in Bloomsbury as a home for the new British Museum, opening it to the public for the first time on 15 January 1759.  The ceiling of the smaller North Hall consists of 36 panels, 18 of which depict plants growing in the British Isles.   [123] Along with Magnolia auriculata, this was one of the two sample images that persuaded Ayrton to authorise the painted ceiling.}
\expandafter\newcommand\csname myqq94\endcsname{ Towards his death he claimed that by studying as much of the world as possible he hoped to have a closer understanding of the will of God, but there is little evidence that he was particularly pious during most of the period in which he assembled his collections.}
\expandafter\newcommand\csname myqq95\endcsname{ [133] As a cultivated fruit developed by agricultural selection, the apple also symbolised human dominance over nature.  1 Metal carbonyls, nitrosyls, and isocyanides
 State Road 2 also provided an important connection between the Arkansas Timberlands, approximately the western half of its Arkansas alignment, and the Arkansas Delta on the eastern half of the state. }
\expandafter\newcommand\csname myqq96\endcsname{ Once penetrated, the blood is sucked up the food channel by a mechanism located in the louse's head.  Waterhouse's design was a Romanesque scheme,[42] loosely based on German religious architecture;[43] Owen was a leading creationist, and felt that the museum served a religious purpose in displaying the works of God.}
\expandafter\newcommand\csname myqq97\endcsname{ A tiny proportion of the global sunflower crop is directly eaten as “nuts” or kernels.  
 If a hog louse is ever removed from its host, the louse typically survives for only 2–3 days.}
\expandafter\newcommand\csname myqq98\endcsname{ Epilobium Angustifolium, rosebay willowherb (also known as Chamaenerion angustifolium)[182] was at the time the museum was built a relatively uncommon plant, found primarily in rocky uplands.  This electron-transfer (i) strengthens the metal–C bond and (ii) weakens the C–O bond.}
\expandafter\newcommand\csname myqq99\endcsname{ [100] Gamboge trees were the traditional source of gamboge, the dark yellow pigment of the clothing worn by Buddhist monks.}
\expandafter\newcommand\csname myqq100\endcsname{ Imported to Europe in large quantities, it became a hugely popular ornamental plant.}
\expandafter\newcommand\csname myqq101\endcsname{ These plants are remarkably diverse in appearance, including variation for head size, color, leaf shape, height.   For example, the Data Protection Commissioner shall investigate any complaint made to him about the contravention of the Data Protection Acts, unless he is of the opinion that it is frivolous or vexatious [4] and the head of a government department may refuse access to records under the Freedom of Information Act if the request is frivolous or vexatious.  Montagu House at the time of its transfer to the newly created British Museum}
\expandafter\newcommand\csname myqq102\endcsname{ Lonicera periclymenum, woodbine or common honeysuckle,[171] is highly valued as an ornamental plant, and has one of the sweetest floral scents of any native British plant.  Of the outer two rows, in the six blocks at the southern end of the hall above the landing and the main entrance (1–18 and 109–126) each panel depicts a different plant considered of particular significance to the British Empire,[83] while the twelve six-panel blocks above the main hall (19–54 and 127–162) each depict a single plant considered of particular importance to visitors or to the history of the museum, spreading across six panels.}
\expandafter\newcommand\csname myqq103\endcsname{ The uppermost three panels in each block consist of what Waterhouse termed "archaic" panels, depicting stylised plants on a green background.   [90] Knapp \& Press (2005) speculate that the apparent lack of public interest in the design of the ceiling could be owing to the prevalence of William Morris's ornate floral wallpaper and fabric designs rendering the decorations of the ceiling less unusual to Victorian audiences than might be expected.}
\expandafter\newcommand\csname myqq104\endcsname{ The ceilings of the Natural History Museum are a pair of decorated ceilings in the main Central Hall (officially Hintze Hall since 2014) and smaller North Hall of the Natural History Museum in South Kensington, London unveiled at the building's opening in 1881. }
\expandafter\newcommand\csname myqq105\endcsname{ Banksia speciosa, the showy banksia,[129] was an Australian plant that was rarely grown in Britain, and was unlikely to be familiar to British audiences.   [151] The establishment of European-controlled treaty ports in the wake of China's defeat made it significantly easier for European merchants to visit China and for Europeans to smuggle items out of China.  4] Sows can be treated with avermectin, a common therapy treating arthropods and nematodes, prior to farrowing to keep lice from moving to younger hogs.}
\expandafter\newcommand\csname myqq106\endcsname{ The ceiling of the smaller North Hall consists of 36 panels, 18 of which depict plants growing in the British Isles. }
\expandafter\newcommand\csname myqq107\endcsname{ In the case of metal-alkenes and alkynes, the strengthening of the M–C2R4 and M–C2R2 bond is reflected in bending of the C–C–R angles which assume greater sp3 and sp2 character, respectively.}
\expandafter\newcommand\csname myqq108\endcsname{ [140] Knapp \& Press (2005) contend that this tree, with which British visitors were unlikely to have been familiar, was intentionally included among more familiar plants as a device to attract the attention of viewers.}
\expandafter\newcommand\csname myqq109\endcsname{ Sunflower seed in the context of global oilseed production (FAO data)
 [33]) In October 1861 Owen gave William Ewart Gladstone, the newly appointed Chancellor of the Exchequer, a tour of the cramped natural history departments of the British Museum, to demonstrate how overcrowded and poorly lit the museum's galleries and storerooms were, and to impress on him the need for a much larger building.}
\expandafter\newcommand\csname myqq110\endcsname{ "Memory Eternal" is chanted at the end of services on Saturdays of the Dead, though not for an individual, but for all of the faithful departed. }
\expandafter\newcommand\csname myqq111\endcsname{ [89][Q] Much was written at the time of the museum's opening about the terracotta decorations of the museum, but very little was written about how the ceiling was received.  [132] Although peaches do not grow well in Britain, they were nonetheless a popular fruit at the time.}
\expandafter\newcommand\csname myqq112\endcsname{ [5] It is known as Sqump to its regulars, the Square and Compass was popular amongst the Telecommunications Research Establishment scientists in Purbeck, who knew the inn as Sine and Cosine.  Quercus robur, the English oak,[136] was considered a national symbol of England.}
\expandafter\newcommand\csname myqq113\endcsname{ A northern lobby ceiling depicting birds, insects, butterflies and paterae}
\expandafter\newcommand\csname myqq114\endcsname{ The pub is named after Square and Compasses, the tools used by carpenters and stonemasons.}
\expandafter\newcommand\csname myqq115\endcsname{ [62] As a consequence, it posed a difficulty to Waterhouse's plans to decorate the building. }
\expandafter\newcommand\csname myqq116\endcsname{ "Memory eternal" is not chanted for those who have been officially glorified (canonized) as saints.}
\expandafter\newcommand\csname myqq117\endcsname{ [177] As a species able to grow in rocky areas and to propagate quickly via rhizomes into areas cleared of other species by burning, during the Second World War it spread rapidly in urban areas destroyed by bombing,[177] gaining rosebay willowherb the nickname of "fireweed" by which it remains frequently known.  The life cycle is completed in about 5 weeks.}
\expandafter\newcommand\csname myqq118\endcsname{ [121] In 19th-century Britain strychnine, produced from the tree's fruit, was one of the most commonly used poisons, and of high commercial significance as a rodenticide.  Melanorrhœa usitata, Burmese lacquer (now known as Gluta usitata), was traditionally used as a source of varnish in Burma.}
\expandafter\newcommand\csname myqq119\endcsname{ As they mature, they move to other areas on the host's body, primarily the abdominal region.[ Jouventin and colleagues conducted exploratory tests on baboons in 1977 that suggested this was possible.}
\expandafter\newcommand\csname myqq120\endcsname{ [96] A specialised hoist is regularly used to allow a surveyor to take high resolution photographs of each panel from a close distance, and the images of each panel used to create a time series for each panel.}
\expandafter\newcommand\csname myqq121\endcsname{ [33]) In October 1861 Owen gave William Ewart Gladstone, the newly appointed Chancellor of the Exchequer, a tour of the cramped natural history departments of the British Museum, to demonstrate how overcrowded and poorly lit the museum's galleries and storerooms were, and to impress on him the need for a much larger building.}
\expandafter\newcommand\csname myqq122\endcsname{ They were former presidential envoy to the Imereti region Temur Shashiashvili, leader of the Lawyers of Georgia Party Kartlos Garibashvili, one of the leaders of the political organization Mdzleveli, Zurab Kelekhsashvili, the President of the Coalition of Non-Government Organisations of the Disabled Zaza Sikharulidze, and leader of the David Agmashenebeli Party Roin Liparteliani. 
 [89][Q] Much was written at the time of the museum's opening about the terracotta decorations of the museum, but very little was written about how the ceiling was received.}
\expandafter\newcommand\csname myqq123\endcsname{ The chief idea to be represented is that of growth.   One of the identical twin balconies running the length of Central Hall, connecting the first and second staircases}
\expandafter\newcommand\csname myqq124\endcsname{ [77][78] Unlike the six-panel sets the archaic panels are not labelled, and while some plants on the archaic panels are recognisable others are stylised beyond recognition.  Montagu House at the time of its transfer to the newly created British Museum
 The IFC was funded by grants from the three governing bodies. 
 [112] Bergamot is commonly used in perfume,[119] and also gives Earl Grey tea its distinctive flavour and scent.}
\expandafter\newcommand\csname myqq125\endcsname{ Montagu House at the time of its transfer to the newly created British Museum
 5] It was one of six districts of Mid Glamorgan, and in 1996 was merged into the larger unitary authority of Rhondda Cynon Taf. }
\expandafter\newcommand\csname myqq126\endcsname{ From 1974 to 1996 the Borough of Cynon Valley was one of thirty-seven districts of Wales.}
\expandafter\newcommand\csname myqq127\endcsname{ Compounds where π backbonding occurs include Ni(CO)4 and Zeise's salt.}
\expandafter\newcommand\csname myqq128\endcsname{ The nearby outbuildings which are of a similar construction have been converted to include garage doors. }
\expandafter\newcommand\csname myqq129\endcsname{ Three long rows of panels on each side rise from the skylights to meet at the roof's apex. }
\expandafter\newcommand\csname myqq130\endcsname{ [106] In an effort to make the Colony of Virginia economically self-sufficient, settler John Rolfe began to plant seeds of the milder and better-tasting Nicotiana tabacum imported from Spanish colonies to the south.}
\expandafter\newcommand\csname myqq131\endcsname{ 4] Sows can be treated with avermectin, a common therapy treating arthropods and nematodes, prior to farrowing to keep lice from moving to younger hogs.[ [83] These each represent a plant considered of particular significance to the British Empire.}
\expandafter\newcommand\csname myqq132\endcsname{ suis spend most of their time in and around the head region of the hog, specifically the ears.  It is likely that he orchestrated its writing.}
\expandafter\newcommand\csname myqq133\endcsname{ The confluence of Kochechum and Nizhnyaya Tunguska corresponds to the farthest point of fairway section upstream off the Yenisey. 
 [178] One of its active ingredients, digitoxin, was the most significant drug for cardiac conditions at the time the museum was built.}
\expandafter\newcommand\csname myqq134\endcsname{ 5] U.S. 82 was rerouted south of Lake Chicot when the Benjamin G.}
\expandafter\newcommand\csname myqq135\endcsname{ Other than on the outermost edges of the panels at the two ends of the hall,[74] each set of nine panels is flanked alongside the girders by an almost abstract design of leaves; these decorations continue along the space between the skylights and the girders to reach the terracotta walls below, providing a visible connection between the walls and the ceiling designs.  A case is frivolous if it has no reasonable chance of succeeding, and is vexatious if it would bring hardship on the opposite party to defend something which cannot succeed.}
\expandafter\newcommand\csname myqq136\endcsname{ Avoiding annual tillage is one of the main motivations for developing perennial grain crops.  }
\expandafter\newcommand\csname myqq137\endcsname{ [84] The central (highest) rows on each side consist of plain green panels, each containing a heraldic rose, thistle or shamrock in representation of England, Scotland and Ireland, the three nations then constituting the United Kingdom.}
\expandafter\newcommand\csname myqq138\endcsname{ Within the labrum are four thin, retractable, perforating stylets (the fascicle) used for capillary sucking in the front.[ However, they would have been familiar to the museum's visitors, as olives were frequently mentioned in the Bible, and olive oil was often used as holy oil by the Anglican Church.  One of the identical twin balconies running the length of Central Hall, connecting the first and second staircases
 Towards his death he claimed that by studying as much of the world as possible he hoped to have a closer understanding of the will of God, but there is little evidence that he was particularly pious during most of the period in which he assembled his collections.}
\expandafter\newcommand\csname myqq139\endcsname{ At the same time, π-backbonding lowers the νCN.  [173] It grows on rough ground, particularly along roads, railways and the edges of fields.  As the skylights were lower than the ceiling the roof was in relative darkness compared to the rest of the room,[46] and owing to the routes to be taken by visitors, the design needed to be attractive when viewed both from the floor below, and from the raised balconies to the each side.  Thus, strong π backbonding ligands are tetrafluoroethylene, tetracyanoethylene, and hexafluoro-2-butyne. }
\expandafter\newcommand\csname myqq140\endcsname{ A terracotta monkey on a supporting column in the Central Hall
 As with the olive, figs and fig-leaves would have been familiar to 19th-century British visitors from the Biblical narrative;[140] 19th-century visitors would likely have recognised the fig tree from its leaves rather than its fruit, owing to the use of fig-leaves in most depictions of Adam and Eve.  Plant breeders at The University of Minnesota have made similar tetraploid hybrids [1] }
\expandafter\newcommand\csname myqq141\endcsname{ In law, frivolous or vexatious, is a term used to challenge a complaint or a legal proceeding being heard, or to deny or dismiss or strike out any ensuing judicial or non-judicial processes.  
 "Memory Eternal" is chanted at the end of services on Saturdays of the Dead, though not for an individual, but for all of the faithful departed. 
 Humphreys Bridge opened in 1940, and retained most of that alignment for the current Greenville Bridge.}
\expandafter\newcommand\csname myqq142\endcsname{ Corylus avellana, common hazel,[171] is one of the most widely grown varieties used for commercial hazelnut production.}
\expandafter\newcommand\csname myqq143\endcsname{ Diospyros embryopteris, the guab tree or Malabar ebony, a traditional source of black dye.  The natural history collections had originally shared a building with their parent institution the British Museum, but with the expansion of the British Empire there was a significant increase in both public and commercial interest in natural history, and in the number of specimens added to the museum's natural history collections. }
\expandafter\newcommand\csname myqq144\endcsname{ [154] Although native to Africa, it had spread throughout tropical regions, and at the time was thought to originate in India.}
\expandafter\newcommand\csname myqq145\endcsname{ Only if none of the named institutions were willing to purchase the collection were the trustees to allow it to be broken up.}
\expandafter\newcommand\csname myqq146\endcsname{ Researchers at The Land Institute have made many tetraploid hybrids like the ones shown here.   [123] Its distinctive fruit would have been immediately recognisable to 19th-century viewers, serving to attract viewers to examine the ceiling more closely.}
\expandafter\newcommand\csname myqq147\endcsname{ Because it is a permanent parasite, the hog louse will only leave its host to move to another host, always swine.  — Richard Owen, President's Address to the British Association for the Advancement of Science, 1858[31]}
\expandafter\newcommand\csname myqq148\endcsname{ [173] It grows on rough ground, particularly along roads, railways and the edges of fields.}
\expandafter\newcommand\csname myqq149\endcsname{ Unlike the intentionally exposed girders of the main hall, the supporting arches above the landing are enclosed within terracotta facing. 
 [65] To create the painted panels from the initial cartoons, Waterhouse commissioned Manchester artist Charles James Lea of Best \& Lea, with whom he had already worked on Pilmore Hall in Hurworth-on-Tees.}
\expandafter\newcommand\csname myqq150\endcsname{ As part of the glorification process for new saints, on the eve of the day before their glorification, "Memory eternal" will be chanted for them at the end of a solemn service known as the "Last Requiem".  A terracotta monkey on a supporting column in the Central Hall}
\expandafter\newcommand\csname myqq151\endcsname{ [74] Owing to the flattened nature of the designs, it is possible that they were based on pressed flowers in the museum's herbarium, or on illustrations in the British Museum's collection of books on botany.  Over 115 species or some 18\% of snakes in the New World are within this mimicry system.}
\expandafter\newcommand\csname myqq152\endcsname{ [86][M] Uniquely in the building, the ceiling panels of the North Hall make use of silver leaf as well as gilt.}
\expandafter\newcommand\csname myqq153\endcsname{ 1 Deterioration, restoration and conservation
 [162] The Maluku Islands were controlled by the Dutch,[V] but in 1810 during the Napoleonic Wars British troops briefly captured the Banda Islands, seizing nutmeg trees which they subsequently planted in Ceylon.  [13] Newman was initially instructed to dismantle the sculpture by Purbeck District Council after a complaint from the public, as the field is within the Area of Outstanding Natural Beauty and did not meet planning regulations. }
\expandafter\newcommand\csname myqq154\endcsname{ In the Russian Orthodox Church, "Memory Eternal" is chanted on the Sunday of Orthodoxy for all of the departed rulers of Russia. 
 [5][B] During Sloane's life there were few public museums in England, and by 1710 Sloane's collection filled 11 large rooms, which he allowed the public to visit.}
\expandafter\newcommand\csname myqq155\endcsname{ 5] It was one of six districts of Mid Glamorgan, and in 1996 was merged into the larger unitary authority of Rhondda Cynon Taf. }
\expandafter\newcommand\csname myqq156\endcsname{ Datura stramonium, jimsonweed or thornapple,[176][179] is the only neophyte species (a species introduced after 1500 that now grows wild) represented on the North Hall ceiling.  Butea frondosa, flame-of-the-forest or dhaak,[112] an Indian plant whose sap was an important source of tannin.}
\expandafter\newcommand\csname myqq157\endcsname{ Memory Eternal[a] is an exclamation, an encomium like the polychronion, used at the end of an Eastern Orthodox funeral or memorial service.}
\expandafter\newcommand\csname myqq158\endcsname{ [174] A commonly found weed, jimsonweed contains high levels of hyoscine (scopolamine), and at the time the museum was built was used as a herbal remedy for asthma and motion sickness.  [121] As an Asian plant that would grow in the British climate, it was a popular ornamental plant in the 19th century.}
\expandafter\newcommand\csname myqq159\endcsname{ [171] A source of glaucine,[185] it is used as a cough suppressant.}
\expandafter\newcommand\csname myqq160\endcsname{ She learns through this situation to not let her tics control her life. }
\expandafter\newcommand\csname myqq161\endcsname{ "Frivolous" and "vexatious" generally mean different things, however both are typically grouped together as they relate to the same basic concept of a complaint or claim not being brought in good faith: }
\expandafter\newcommand\csname myqq162\endcsname{ Alive and Ticking (German: Ein Tick anders) is a German comedy film directed by Andi Rogenhagen.   Saakashvili was inaugurated as President in Tbilisi on January 25, 2004. }
\expandafter\newcommand\csname myqq163\endcsname{ Often a "frivolous" claim is one about a matter so trivial, one so meritless on its face, or one without substance that investigation would be disproportionate in terms of time and cost.   Global uses of sunflower seed (from FAO data)
 One of the identical twin balconies running the length of Central Hall, connecting the first and second staircases}
\expandafter\newcommand\csname myqq164\endcsname{ [100] Gamboge trees were the traditional source of gamboge, the dark yellow pigment of the clothing worn by Buddhist monks.  A vexatious claim or complaint is one (or a series of many) that is specifically being pressed on to cause an act of harassment, annoyance, frustration, worry, or even bring financial cost (such as engage a defence lawyer) to their defendant or respondent.}
\expandafter\newcommand\csname myqq165\endcsname{ Knapp \& Press (2005) conjecture that the quince was included to allow visitors to compare a familiar plant with those more exotic species also depicted on the ceiling.}
\expandafter\newcommand\csname myqq166\endcsname{ 7] Oxidation of R3P–M complexes results in longer M–P bonds and shorter P–C bonds, consistent with π-backbonding.}
\expandafter\newcommand\csname myqq167\endcsname{ •  •  Joseph Banks had accompanied Captain James Cook on his voyage to Australia. }
\expandafter\newcommand\csname myqq168\endcsname{ Being above the skylights meant that the ceiling was dimly lit.   While the term is referenced in laws and regulations, it is often not defined by statute, being developed instead by decisions of the courts.  
 "Memory Eternal" is intoned by the deacon and then chanted by all in response three times during the liturgy on the Sunday of Orthodoxy to commemorate church hierarchs, Orthodox monarchs, Orthodox patriarchs and clergy, and all deceased Orthodox Christians [2] }
\expandafter\newcommand\csname myqq169\endcsname{ [96] This permits staff to monitor the condition of each panel for deterioration.}
\expandafter\newcommand\csname myqq170\endcsname{ [161] Indigenous to the Maluku Islands (the Moluccas), it had historically been imported to Europe via land across Asia to the Ottoman Empire and onwards to Venice, and consequently was extremely scarce and expensive; it was the search for new routes to nutmeg markets that prompted the voyages of Vasco da Gama to India,[161] of Christopher Columbus to the Americas,[161] and of John Franklin to the Northwest Passage.}
\expandafter\newcommand\csname myqq171\endcsname{ Sunflower seed in the context of global oilseed production (FAO data)}
\expandafter\newcommand\csname myqq172\endcsname{ 1] On July 1, 1931, the route was entirely replaced by US Highway 82 (US 82) by the American Association of State Highway Officials (AASHTO).  The ceiling of the smaller North Hall consists of 36 panels, 18 of which depict plants growing in the British Isles. }
\expandafter\newcommand\csname myqq173\endcsname{ Georgian law requires a 50\% turnout for elections to be valid.  After an online petition, the council decided that the structure could remain for two years.  Aberdare is located in the north of the valley and Mountain Ash is in the south of the valley. }
\expandafter\newcommand\csname myqq174\endcsname{ [5] It is known as Sqump to its regulars, the Square and Compass was popular amongst the Telecommunications Research Establishment scientists in Purbeck, who knew the inn as Sine and Cosine.}
\expandafter\newcommand\csname myqq175\endcsname{ [1] Built in the 18th century as a pair of cottages before becoming a public house, the Square and Compass got its name in 1830 from a landlord who had been a stonemason.   The Kochechum (Russian: Кочечум) is a river in Siberia, Russia, it flows through the Syverma Plateau in Krasnoyarsk Krai.}
\expandafter\newcommand\csname myqq176\endcsname{ With more space for displays and able to accommodate large numbers of visitors, the new British Museum proved a success with the public, and the natural history department proved particularly popular.}
\expandafter\newcommand\csname myqq177\endcsname{ 1 Metal carbonyls, nitrosyls, and isocyanides
 In law, frivolous or vexatious, is a term used to challenge a complaint or a legal proceeding being heard, or to deny or dismiss or strike out any ensuing judicial or non-judicial processes.  }
\expandafter\newcommand\csname myqq178\endcsname{ Coleg Morgannwg has a campus in the Cynon Valley based in Cwmdare. 
 Unlike the cavernous, intentionally cathedral-like feel of the main space of the Central Hall,[68] the ceiling of the landing above the main entrance, connecting the balconies to the upper level, has a different design.  The idea seems to have been suggested by the Reference Library of 60,000 volumes in the Reading Room of the British Museum, which this hall will almost equal in size, though of a very different form. }
\expandafter\newcommand\csname myqq179\endcsname{ suis are not usually lethal to the hosts, but major economic losses are ascribed to impaired growth, general irritation, and immune responses to the lice.  The colours will be arranged so that the most brilliant will be near the apex of the roof. }
\expandafter\newcommand\csname myqq180\endcsname{ [121] As an Asian plant that would grow in the British climate, it was a popular ornamental plant in the 19th century.}
\expandafter\newcommand\csname myqq181\endcsname{ In this case, other organisms could benefit from this programming, and Batesian or Müllerian mimics of it could potentially evolve.[ [112] Balsam of Peru was a significant ingredient in perfumes and was also a commonly used food flavouring and traditional medication.}
\expandafter\newcommand\csname myqq182\endcsname{ Sambucus nigra, elder,[176] was a common ornamental plant. }
\expandafter\newcommand\csname myqq183\endcsname{ [156] (The scientific name Blighia sapida had been given to the ackee by staff at the British Museum, so the museum's staff would certainly have been aware of the correct name.   suis is the paratergal plates lining the sides of each segment of the abdomen.}
\expandafter\newcommand\csname myqq184\endcsname{ Tubers are storage organs and are modified rhizomes.  }
\expandafter\newcommand\csname myqq185\endcsname{ [8] It is one of just nine pubs, known as the 'Perfect Nine', to have featured in all 37 editions of CAMRA's Good Beer Guide.  •  •  The museum eventually opened a more coherent display on the natural history of Britain in a second floor gallery.}
\expandafter\newcommand\csname myqq186\endcsname{ [133] As a cultivated fruit developed by agricultural selection, the apple also symbolised human dominance over nature.}
\expandafter\newcommand\csname myqq187\endcsname{ Globally, sunflowers are the fourth most important oil crop.   [44] The design was centred around a very large rectangular central hall and a smaller hall to the north.}
\expandafter\newcommand\csname myqq188\endcsname{ [133] As a cultivated fruit developed by agricultural selection, the apple also symbolised human dominance over nature.}
\expandafter\newcommand\csname myqq189\endcsname{ Each of the lower six panels in each block depicts a plant considered of particular significance to the British Empire, against a pale background. }

