\documentclass{article}

\input{wikilipsum.tex}

\newcommand\cmdwl[1]{\texttt{\textbackslash #1}}


\begin{document}
\begin{center}
\bfseries wikilipsum\\
 Tutorial
\end{center}
This package provides the \cmdwl{wikilipsum} command for printing lipsum-like stored text manually selected from (English-language) Wikipedia.\footnote{As at 2020-08-01.} 

For usage, place the files  \texttt{wikilipsum.tex} (the commands) and \texttt{wikilipsum1.tex} (the texts) in a location where \TeX\ can find them, and then use 
\begin{quotation}
\texttt{\cmdwl{input}\{wikilipsum.tex\}} 
\end{quotation}
in the preamble to make the wikilipsum available.
\bigskip

\textbf{Default}

Default setting (the command with no start and finish paragraph numbers) prints the second paragraph.

\cmdwl{wikilipsum} produces:

\begin{quotation}\sffamily\small
\wikilipsum
\end{quotation}
\bigskip

\textbf{Single Paragraph}

Specifiying a paragraph number (maximum of \maxwikilipsum) as both \textit{start} and \textit{finish} prints just that paragraph.

\cmdwl{wikilipsum[1-1]} produces:
\begin{quotation}\sffamily\small
\wikilipsum[1-1]
\end{quotation}
\bigskip

\textbf{Range}

Specifying a range of paragraphs ([\textit{start}-\textit{finish}]) prints the corresponding paragraphs.

\cmdwl{wikilipsum[1-3]} produces:
\begin{quotation}\sffamily\small
\wikilipsum[1-3]
\end{quotation}


\textbf{Setting}

Each paragraph text is preceded and followed by whatever code is stored in \cmdwl{lipsumwikipresep} and \cmdwl{lipsumwikisep}. Default code is nothing, and \cmdwl{par}, respectively. To print the paragraph range 1-3 as continuous text, for example, do:
\begin{quotation}
\texttt{\textbackslash renewcommand\textbackslash lipsumwikisep\{\}}\par
\cmdwl{wikilipsum[1-3]}, which produces:\par
\begin{quotation}\sffamily\small\renewcommand\lipsumwikisep{}\wikilipsum[1-3]\end{quotation}
\end{quotation}

\textbf{Backwards}

The \textit{start} paragraph number can be higher than the \textit{finish}.
\begin{quotation}
\texttt{\textbackslash renewcommand\textbackslash lipsumwikipresep\{>> \}}\par
\texttt{\textbackslash renewcommand\textbackslash lipsumwikisep\{ << (\textbackslash x)\textbackslash par\}\scriptsize{\%\textbackslash x=par num}}\par
\cmdwl{wikilipsum[3-1]}\par produces:\par
\begin{quotation}\sffamily\small
\renewcommand\lipsumwikipresep{>> }
\renewcommand\lipsumwikisep{ << (\x)\par}
\wikilipsum[3-1]
\end{quotation}
\end{quotation}

\textbf{Random}

\cmdwl{randomwikilipsum\{x\}} will typeset a set of $x$ random paragraphs.

\begin{quotation}
\cmdwl{randomwikilipsum\{3\}}\par produced:\par
\begin{quotation}\sffamily\small
\randomwikilipsum{3}
\end{quotation}
\end{quotation}



\bigskip
\bigskip

\hfill ***\hfill\ 

\end{document}



